What can Issues on GitHub and Google Code tell us about Bug Hazards in Android and Java?

### 2015-02-14 android-stacks.tex
Small changes to best practices II.C

Several general guidelines have been proposed on how to use Java
exceptions~\cite{mandrioli1992advances,gosling2000java,wirfs2006toward,
bloch2008effective}. Such guidelines do not focus on 
advocating any specific exception type, but rather propose ways to effectively use each of them.
 We compiled a list of the guidelines related to exception types in Java, 
summarized below\footnote{We also compiled aditional guidelines related
to ways of handling exceptions but they are out of the scope of this paper.}:

@@

%\textbf{I
\emph{I-Checked exceptions should be used to represent recoverable
conditions} (\cite{mandrioli1992advances,gosling2000java,wirfs2006toward,bloch2008effective}).
The developer should use checked exceptions for conditions from which the caller
is expected to recover. By confronting the API user with a checked exception,
the API designer is forcing the client to handle the exceptional condition. The
client can explicitly ignore the exception (swallowing, or converting it to
other type) at the expense of the program's robustness~\cite{gosling2000java}.

\emph{II-Error represents an unrecoverable conditions which should not be handled} 
(\cite{gosling2000java}).  Errors should result from failures detected
by the runtime environment which indicate resource deficiencies, invariant
failures or other conditions, that make impossible for the program to recover.

@@

\emph{III-A method should throw exceptions that precisely define the
exceptional condition} (\cite{gosling2000java,bloch2008effective}). To do so,
developers should either try to reuse the exception types already defined in the
Java API or they should create a specific exception. Throwing general types such as a
pure java.lang.Exception or a java.lang.RuntimeException is considered a bad practice.

@@

\emph{IV- All exceptions explicitly thrown by reusable code should be documented.}
(\cite{mandrioli1992advances,gosling2000java,wirfs2006toward,bloch2008effective}).
The exceptions thrown by a method are an important part of methods interface,
and is required to use the method properly. The checked exceptions are already
part of the  methods signature, and the method caller is aware of the checked
exceptions being thrown by it. According to~\cite{bloch2008effective}, it is
also wise to document (either on the \emph{exception interface} or using @throws tag on Javadoc) 
the \emph{explicitly thrown} runtime exceptions as carefully as checked exceptions. 
The \emph{explicitly thrown} exceptions exclude the ones implicitly 
thrown by the runtime environment due to programming
mistakes. Such practice is mostly needed when developing library/framework 
code reusable code - as the developers do not have access to the source code. 
Doing so, the clients of such library/framework
will be aware of all the exceptions a method can throw and can design the code
to deal with them ~\cite{Robil00}. If the developer fails to follow this practice 
 it will be difficult or even impossible for the caller to 
make effective use of such method~\cite{wirfs2006toward, bloch2008effective},
and protect the system against unforeseen exceptions thrown by the utility code. 
Such exceptions can lead to the uncaught exceptions - one of the main causes of 
systems crashes.

>>>>

Several general guidelines have been proposed on how to use Java
exceptions~\cite{mandrioli1992advances,gosling2000java,wirfs2006toward,
bloch2008effective}. Such guidelines do not
advocate any specific exception type, but rather propose ways to effectively use each of them.
Based on these, for the purpose of our analysis we compiled the following list of Java exception handling best practices.

@@

\emph{I-Checked exceptions should be used to represent recoverable
conditions} (\cite{mandrioli1992advances,gosling2000java,wirfs2006toward,bloch2008effective}).
The developer should use checked exceptions for conditions from which the caller
is expected to recover. By confronting the API user with a checked exception,
the API designer is forcing the client to handle the exceptional condition. The
client can explicitly ignore the exception (swallowing, or converting it to
another type) at the expense of the program's robustness~\cite{gosling2000java}.

\emph{II-Error represents an unrecoverable condition which should not be handled} 
(\cite{gosling2000java}).  Errors should result from failures detected
by the runtime environment which indicate resource deficiencies, invariant
failures or other conditions, from which the program cannot possibly recover.

@@

\emph{III-A method should throw exceptions that precisely define the
exceptional condition} (\cite{gosling2000java,bloch2008effective}). To do so,
developers should either try to reuse the exception types already defined in the
Java API or they should create a specific exception. Thus, throwing general types such as a
pure java.lang.Exception or a java.lang.RuntimeException is considered bad practice.

@@

\emph{IV- All exceptions explicitly thrown by reusable code should be documented.}
(\cite{mandrioli1992advances,gosling2000java,wirfs2006toward,bloch2008effective}).
The exceptions thrown by a method are an important part of its interface,
since knowledge of them is required to use a method properly. 
Checked exceptions are already
part of the  method signature, making the method caller aware of the checked
exceptions it may have to handle.

According to~\cite{bloch2008effective}, it is
also wise to document (either on the \emph{exception interface} or using the @throws tag in Javadoc) 
the \emph{explicitly thrown} runtime exceptions as carefully as checked exceptions. 
These \emph{explicitly thrown} exceptions exclude the ones implicitly 
thrown by the runtime environment due to programming
mistakes.

This practice is mostly needed when developing  working with library/framework 
code -- as the developers do not have access to the source code. 
Doing so, the clients of such a library/framework
will be aware of all the exceptions a method can throw and can design the code
to deal with them ~\cite{Robil00}. If the developer fails to follow this practice 
 it will be difficult or even impossible for the caller to 
make effective use of such a method~\cite{wirfs2006toward, bloch2008effective},
and protect the system against unforeseen exceptions thrown by the utility code. 
This can lead to uncaught exceptions - one of the main causes of 
systems crashes.
